\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-20 WOOT/Files/experiment.tex
exp,coutermeasure,util
Remove cv code

In the privacy extraction mode experiment, ``HUAWEI P30'', a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, is chosen as the target device. 
First, we connect \tool to the target device. As remote control mode, \tool capture video from the victim's device and use ``opencv'' to identify ``valuable'' information from video stream. When the victim views text or photoes with text, \tool can use optical character recognition (OCR) to extract text from corresponding video frames. \yechang{hyperlink to OCR?}
For example, extracting the victim's name, photo, address, and ID number when victim is viewing his or her photos of his or her ID card or passport documents,
extracting the victim's payment information when victim is using bank apps or payment apps. Besides, \tool can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
Here is an example of extracting payment code with opencv library in listing~\ref{lst2:qr},

@@

\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
import cv2, qrcode,requests
import pyzbar.pyzbar as pyzbar
def decodeDisplay(video):
    gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
    barcodes = pyzbar.decode(gray)
    for barcode in barcodes:
        barData = barcode.data.decode()
        barType = barcode.type
        requests.post('<server of attacker>',
            data={
                'data': barData,
                'type': barType
            }
        )
if __name__ == '__main__':
    cam = cv2.VideoCapture(0)
    while True:
        ret, frame = cam.read()
        decodeDisplay(frame)
        if cv2.waitKey(5) == 27:
            break
    cam.release()
    cv2.destroyAllWindows()
\end{lstlisting}

@@

\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information extracted}
	\label{table:information_extracted}
\end{table*}

>>>>

In the privacy extraction mode experiment, ``HUAWEI P30'', a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, is chosen as the target device. 
First, we connect \tool to the target device. As remote control mode, \tool capture video from the victim's device and use ``opencv'' to identify ``valuable'' information from video stream. When the victim views text or photoes with text, \tool can use optical character recognition (OCR) to extract text from corresponding video frames. \yechang{hyperlink to OCR?}
For example, extracting the victim's name, photo, address, and ID number when victim is viewing his or her photos of his or her ID card or passport documents,
extracting the victim's payment information when victim is using bank apps or payment apps. Besides, \tool can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
Here is an example of extracting payment code with opencv library in listing. \shuqing{Need to be modified.}

@@

%\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
%import cv2, qrcode,requests
%import pyzbar.pyzbar as pyzbar
%def decodeDisplay(video):
%    gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
%    barcodes = pyzbar.decode(gray)
%    for barcode in barcodes:
%        barData = barcode.data.decode()
%        barType = barcode.type
%        requests.post('<server of attacker>',
%            data={
%                'data': barData,
%                'type': barType
%            }
%        )
%if __name__ == '__main__':
%    cam = cv2.VideoCapture(0)
%    while True:
%        ret, frame = cam.read()
%        decodeDisplay(frame)
%        if cv2.waitKey(5) == 27:
%            break
%    cam.release()
%    cv2.destroyAllWindows()
%\end{lstlisting}

@@

\begin{table*}[hbtp]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Application Column  & Application & Private information leaked                       \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information extracted}
	\label{table:information_extracted}
\end{table*}
